Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-25 paper/ms.tex
fixed compilation problem
small changes to ms.tex

We  explore the parameter space of the models
${\mathcal M}$ by  means of the Markov Chain Monte Carlo technique using
the EMCEE python package \citep{emcee2013}.

@@

From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
The $1\sigma$ uncertainty for this median value is estimated from the
$16$ and $84$ percentile values in the $\log M_{50}$ distribution.  
This result is consistent with previous
 estimations of  the  median dark matter halo mass reported by
 \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
 \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
 \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}$) 
using semi-analitical approaches.

@@

\item ALSO MENTION THIS HERE BECAUSE IS A STRONG CONSTRAIN:
 the 1-$\sigma$ width of the mass distribution is highly constrained to be between $0.2$ and $0.6$ dex.

>>>>

We  explore the parameter space of the models
${\mathcal M}$ by  means of the Affine Invariant  Markov Chain Monte Carlo technique using
the EMCEE python package \citep[][and references therein]{emcee2013}.

@@

From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
The $1\sigma$ uncertainty for this median value is estimated from the
$16$ and $84$ percentile values in the $\log M_{50}$ distribution.  
This result is consistent with previous
 estimations of  the  median dark matter halo mass reported by
 \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
 \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
 \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}}$) 
using semi-analitical approaches.   MENTION THAT OUR MASS IS SYSTEMATICALLY LOWER
AND THAT (ONLY IF MAKE SENSE) WE DO NOT DISAGREE  THAT DARK MATTER OF BIELBY AND OTHERS  OF THEIR PARTICULAR FIELDS IRE WRONG, BUT WHEN THE COSMIC VARIANCE IS INCLUDES THAT IMPLIES THAT THA THE MEAIN MASS OF LAES IN THE UNIVERSE IS SMALLER (BECAUSE OF THE ASSIMETRY IN THE NUMBER DENSITY DISTRIBUTION FUNCTION). DO SEMIANALITIC MODELS ASSUME GAUSSIAN DISTRIBUTION OF MATTER PERTURBATIONS?

@@

\item ALSO MENTION THIS HERE BECAUSE IS A STRONG CONSTRAIN:
 the 1-$\sigma$ width of the mass distribution is highly constrained to be between $0.2$ and $0.6$ dex. SOMETHING THAT IS ALSO IMPORTANT IS THAT THIS CONSTRAIN IS ASSUMING OUR MODEL IS RIGHT, IF IT HAPPENS TO BE THAT THE FUNCTION THAT RELATES LUMINOSITY WITH MASS IS VERY STEPPEN THEN THE RESULTS MAY CHANGE.
